\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small#3} & \textit{\small #4} \\
      {\small#5}  \\
      % {\small#6}  \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeEducationHeadingnew}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small#3} & \textit{\small #4} \\
      {\small#5}  \\
      {\small#6}  \\
    \end{tabular*}\vspace{-12pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumePublicationsHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Large \scshape \href{https://livfour.github.io}{Junfeng Li}} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:+8617683881879}{17683881879}
    $|$
    \faAt \hspace{.5pt} \href{mailto:junfeng1287@gmail.com}{junfeng1287@gmail.com}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/Livfour}{GitHub}
    $|$
    \faGraduationCap \hspace{.5pt} \href{https://scholar.google.com/citations?user=X4wV9ucAAAAJ}{Google Scholar}
\end{center}

\vspace{-5pt}
\begin{center}
    \small
    Research Interests: \textbf{Vision-Language-Action (VLA) Models} and \textbf{World Models}.
\end{center}

%----------- EDUCATION & EXPERIENCE -----------

\section{Education \& Experience}
  \resumeSubHeadingListStart

    \resumeEducationHeadingnew
        {Hong Kong University of Science and Technology (Guangzhou)}{Guangzhou, China}
        {Ph.D. Student (Supervised by Prof. \href{https://sites.google.com/view/haoangli/homepage}{Haoang Li})}{Sep. 2025 \textbf{--} Present}
        {Research Focus: Vision-Language-Action (VLA) Models and World Models.}
        {}

    \resumeEducationHeadingnew
        {Hong Kong University of Science and Technology (Guangzhou)}{Guangzhou, China}
        {Research Assistant (with Prof. \href{https://sites.google.com/view/haoangli/homepage}{Haoang Li})}{Jun. 2024 \textbf{--} Apr. 2025}
        {Research Focus: Dynamic 3D/4D scene generation and generative modeling.}
        {}

    \resumeEducationHeadingnew
        {University College London}{London, United Kingdom}
        {Master of Science in Computer Science}
        {Sep. 2022 \textbf{--} Dec. 2023}
        {awarded \textit{with Distinction}, GPA: 3.75/4.25}
        
    \resumeEducationHeadingnew
        {University of Birmingham}{Birmingham, United Kingdom} 
        {Bachelor of Engineering in Mechanical Engineering}
        {Sep. 2019 \textbf{--} Jul. 2021}
        {awarded \textit{with Honours, Class I}, GPA: 3.75/4.25}
        
    \resumeEducationHeading
      {Wuhan University of Technology }{Wuhan, China} 
      {Bachelor of Engineering in Mechanical Engineering}
      {Sep. 2017 \textbf{--} Jun. 2019}
      {GPA: 84/100}

  \resumeSubHeadingListEnd

  \vspace{3pt}

% ----------- PUBLICATIONS -----------

\section{Publications \& Research Experience}
  \vspace{2pt}
  \begin{small}
  \begin{itemize}
    \item[\textbf{[1]}] Zhide Zhong*, \underline{Junfeng Li*}, Junjie He, Haodong Yan,
      Xin Gong, Guanyi Zhao, Yingjie Cai, Jiantao Gao, Xu Yan, Bingbing Liu, Yingcong Chen, Liuqing Yang, Haoang Li,
      ``DualCoT-VLA: Visual-Linguistic Chain of Thought via Parallel Reasoning for Vision-Language-Action Models.''

    \item[\textbf{[2]}] Zhide Zhong, Haodong Yan, \underline{Junfeng Li}, Junjie He, Tianran Zhang, Haoang Li,
      ``VLA-OPD: Bridging Offline SFT and Online RL for Vision-Language-Action Models via On-Policy Distillation.''

    \item[\textbf{[3]}] Zhide Zhong, Haodong Yan, \underline{Junfeng Li}, Xiangchen Liu,
      Xin Gong, Tianran Zhang, Wenxuan Song, Jiayi Chen, Xinhu Zheng, Hesheng Wang, Haoang Li,
      ``FlowVLA: Visual Chain of Thought-based Motion Reasoning for Vision-Language-Action Models,''
      \textit{arXiv preprint arXiv:2508.18269}, 2025.

    \item[\textbf{[4]}] Haodong Yan, Hang Yu, Zhide Zhong, Weilin Yuan, Xin Gong,
      Zehang Luo, Chengxi Heyu, \underline{Junfeng Li}, Wenxuan Song, Shunbo Zhou, Haoang Li,
      ``Open-world Hand-Object Interaction Video Generation Based on Structure and Contact-aware Representation,''
      \textit{IEEE/CVF Conference on Computer Vision and Pattern Recognition (\textbf{CVPR})}, 2025.

    \item[\textbf{[5]}] \underline{Junfeng Li*}, Junjie He*, Wenjie Liu*, Tianyu Huang,
      Shunbo Zhou, Jun Ma, Hesheng Wang, Haoang Li,
      ``SCSV: Spatial-temporal Consistent Dynamic 3D Scene Generation from Sparse Views,''
      \textit{IEEE Transactions on Image Processing (\textbf{TIP})}, 2025.
  \end{itemize}
  \end{small}



%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        
        \textbf{Programming Languages: }{Python, JavaScript/TypeScript, HTML, CSS.} \\ \vspace{3pt}
        
        \textbf{ML/AI Frameworks: }{PyTorch, Hugging Face Transformers, DeepSpeed, vLLM.} \\ \vspace{3pt}

        \textbf{AI-Assisted Development: }{Proficient in AI coding tools (Claude Code, Codex, Cursor) and multi-agent-orchestrated project development.} \\ \vspace{3pt}

        \textbf{DevOps \& Tools: }{Linux, Slurm, Git, Docker.}
        
    }}
  \resumeSubHeadingListEnd


\section{Languages}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        
        \textbf{English: }{Fluent (IELTS 7.0).} \\ \vspace{3pt}
        
        \textbf{Mandarin: }{Native.} \\ \vspace{3pt}
        
    }}
  \resumeSubHeadingListEnd

\end{document}